---
title: "Exam 3"
author: "Samantha Ingram"
date: "2022-11-02"
output: html_document
---
<br>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

**Task 1: Loading packages and the necessary csv file**

```{r}
library(tidyverse)
library(kableExtra)
library(janitor)
library(broom)
library(easystats)

df <- read_csv("./Data/FacultySalaries_1995.csv")

df %>% head %>% kable() %>% kable_classic()

#renaming to make it more readable for plotting. Just something I wanted to do.
dat <- df %>% 
  rename(Full = AvgFullProfSalary,
         Assoc = AvgAssocProfSalary,
         Assist = AvgAssistProfSalary,
         All = AvgProfSalaryAll,
         Comp_Full = AvgFullProfComp,
         Comp_Assoc= AvgAssocProfComp,
         Comp_Assist = AvgAssistProfComp,
         Comp_All = AvgProfCompAll,
         Num_Full = NumFullProfs,
         Num_Assoc = NumAssocProfs,
         Num_Assist = NumAssistProfs)
```

Cleaning up the data set to be in "longer" format:

```{r}
tidy <- dat %>% 
  pivot_longer(cols = Full:All, names_to = "Rank", values_to = "Salary") %>% 
  pivot_longer(cols = Comp_Full:Comp_All, names_to = "Comp_Rank", values_to= "Comp_Salary") %>% 
  pivot_longer(cols= starts_with("Num"), names_to = "Prof_Rank", values_to = "Prof_Count")

```

Plotting the clean data set!

```{r}
tidy %>% 
  unique.data.frame() %>% 
  filter(Rank != "All", Tier != "VIIB") %>% 
  group_by(Rank) %>% 
  ggplot(aes(x=Rank, y=Salary, fill=Rank))+
  geom_boxplot()+
  facet_wrap(~Tier)+
  theme_minimal()+
  theme(axis.text.x = element_text(angle= 45))
```
<br>
<br>


**Task 2: Building an ANOVA model**

```{r}
#building a model that tests the influence of state, tier, and rank on salary.
mod <- aov(data=tidy, formula= Salary ~ State+ Tier+ Rank)
summary(mod)
```
It looks like state, tier and rank all are important factors to consider when it comes to salary.
<br>
<br>

**Task 3: Looking at a new data set "Juniper_Oils"**
```{r}
Juniper <- read_csv("./Data/Juniper_Oils.csv")
Juniper %>% head %>% kable() %>% kable_classic()
```
<br>

Cleaning up the Juniper data set!!
```{r}
tidyjuniper <- Juniper %>% janitor::clean_names() %>% 
  pivot_longer(cols = alpha_pinene:thujopsenal, names_to = "chemical_id", values_to = "concentration")
```

<br>
<br>

**Task 4: Plotting the new "tidyjuniper" data set**
```{r}
    tidyjuniper %>% 
      ggplot(aes(x=years_since_burn, y=concentration))+
      geom_smooth()+
      facet_wrap(~chemical_id, scales = "free")+
  theme_minimal()
```
<br>
<br>

**Task 5: Building a generalized linear model to test chemical compounds that are significant when considering years since burn**
```{r}
junmod <- glm(data=tidyjuniper, formula= concentration~ chemical_id *years_since_burn )
tidy(junmod) %>% 
  filter(p.value<0.05)
```

